Perceived value of video games, but not hours played, predicts mental well-being in adult Nintendo players

### 2024-07-10 ms.qmd
renv minor fix

  - name: Andrew K Przybylski
    corresponding: true
    email: andy.pryzbylski@oii.ox.ac.uk
    orcid: 0000-0003-4126-0696
    affiliations:
      - name: University of Oxford
        department: Oxford Internet Institute
    # roles:
    #   - conceptualization
    #   - funding acquisition
    #   - project administration
    #   - editing
abstract: "Studies on video games and well-being often rely on self-report measures or data from a single game. Here, we study how 703 US adults' time spent playing over 150 1st-party Nintendo Switch games (totaling 140k hours) relates to their life satisfaction, affect, depressive symptoms, and general mental well-being. We replicate previous findings that playtime over the past 2 weeks does not predict well-being, and extend these findings to a wider range of timescales (1 hour to 1 year). Results suggest that relationships, if present, dissipate within 2 hours of gameplay. Our non-causal findings suggest substantial confounding would be needed to shift a meaningful true effect to the observed null. Although playtime was not related to well-being, players’ assessments of the value of game time—so called gaming life fit—was. Results emphasize the importance of defining the gaming population of interest, collecting data from more than one game, and focusing on how players integrate gaming into their lives rather than the amount of time spent."
keywords: [video games, digital trace data, well-being]
author-note:
  # Disclosures condensed to one paragraph, but you can start a field with two line breaks to break them up: \n\nNew Paragraph
  disclosures:
    study-registration: This study was registered on the Open Science Framework (https://osf.io/sjqyt).
    # Acknowledge and cite data/materials to be shared.
    data-sharing: Data and materials are available at https://osf.io/6xkdg/. 
    # Example: [Author name] has been a paid consultant for Corporation X, which funded this study.
    conflict-of-interest: Data for this study was provided by Nintendo of America. Nintendo of America had no role in the design of the study, the analysis of the data, or decision to publish any results. The authors declare no other competing interests. 
    # Example: This study was supported by Grant [Grant Number] from [Funding Source].
    financial-support: This research was supported by Huo Family Foundation and the UK Economic and Social Research Council (ES/W012626/1). KM was supported by Forskningsrå det för hälsa, arbetsliv och välfärd (2021-01284).
    # Example: The authors are grateful to [Person] for [Reason].
    gratitude: ~
    # Example. Because the authors are equal contributors, order of authorship was determined by a fair coin toss.
    authorship-agreements: ~
bibliography: references.bib
floatsintext: true # If true, tables and figures are mingled with the text instead of listed at the end of the document.
numbered-lines: false # Numbered lines (.pdf and .docx only)
meta-analysis: false
suppress-credit-statement: true
format:
  apaquarto-docx: default
    # blank-lines-above-author-note: 0
    # blank-lines-above-title: 1
  # apaquarto-html:
  #   documentmode: man
  #   code-fold: true
  #   code-summary: "Show the code"
  #   wordcount-html: default
  # apaquarto-pdf:
  #   documentmode: jou
---

>>>>

  - name: Andrew K Przybylski
    corresponding: true
    email: andy.pryzbylski@oii.ox.ac.uk
    orcid: 0000-0003-4126-0696
    affiliations:
      - name: University of Oxford
        department: Oxford Internet Institute
    # roles:
    #   - conceptualization
    #   - funding acquisition
    #   - project administration
    #   - editing
abstract: "Studies on video games and well-being often rely on self-report measures or data from a single game. Here, we study how 703 US adults' time spent playing over 150 1st-party Nintendo Switch games (totaling 140k hours) relates to their life satisfaction, affect, depressive symptoms, and general mental well-being. We replicate previous findings that playtime over the past 2 weeks does not predict well-being, and extend these findings to a wider range of timescales (1 hour to 1 year). Results suggest that relationships, if present, dissipate within 2 hours of gameplay. Our non-causal findings suggest substantial confounding would be needed to shift a meaningful true effect to the observed null. Although playtime was not related to well-being, players’ assessments of the value of game time—so called gaming life fit—was. Results emphasize the importance of defining the gaming population of interest, collecting data from more than one game, and focusing on how players integrate gaming into their lives rather than the amount of time spent."
keywords: [video games, digital trace data, well-being]
author-note:
  # Disclosures condensed to one paragraph, but you can start a field with two line breaks to break them up: \n\nNew Paragraph
  disclosures:
    study-registration: This study was registered on the Open Science Framework (https://osf.io/sjqyt).
    # Acknowledge and cite data/materials to be shared.
    data-sharing: Data and materials are available at https://osf.io/6xkdg/. 
    # Example: [Author name] has been a paid consultant for Corporation X, which funded this study.
    conflict-of-interest: Data for this study was provided by Nintendo of America. Nintendo of America had no role in the design of the study, the analysis of the data, or decision to publish any results. The authors declare no other competing interests. 
    # Example: This study was supported by Grant [Grant Number] from [Funding Source].
    financial-support: This research was supported by Huo Family Foundation and the UK Economic and Social Research Council (ES/W012626/1). KM was supported by Forskningsrå det för hälsa, arbetsliv och välfärd (2021-01284).
    # Example: The authors are grateful to [Person] for [Reason].
    gratitude: ~
    # Example. Because the authors are equal contributors, order of authorship was determined by a fair coin toss.
    authorship-agreements: ~
bibliography: references.bib
floatsintext: true # If true, tables and figures are mingled with the text instead of listed at the end of the document.
numbered-lines: false # Numbered lines (.pdf and .docx only)
meta-analysis: false
suppress-credit-statement: true
format:
  # apaquarto-docx: default
    # blank-lines-above-author-note: 0
    # blank-lines-above-title: 1
  # apaquarto-html:
  #   documentmode: man
  #   code-fold: true
  #   code-summary: "Show the code"
  #   wordcount-html: default
  apaquarto-pdf:
    documentmode: jou
---
